The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)

### 2016-06-10 WSSSPE4_proposal/WSSSPE4_proposal.tex
starting to work through changes from 2 to 4

{\bf \noindent Summary:} The WSSSPE4 workshop is part of a community driven effort to address the many new challenges that are evident for the development, deployment and maintenance of reusable software for academic research and education. These challenges include the software development process, the support and maintenance of software, governance and business models particularly for sustainability, the role of software in building science communities, the need for software to lead to science which is verifiable and reproducible, policy issues such as how to measure software impact, choose licensing, or assign software credit, and the education and nurturing of early stage researchers in scientific software. 
Based on a successful WSSSPE 1 meeting at SC13 in Denver in November 2013, the organizers expect over 60 submitted papers and around 150 attendees at the WSSSPE 2 meeting that is anticipated to be held at SC14 in New Orleans in November 2014 (a proposal for a SC14 workshop has been submitted).  As with WSSSPE 1, WSSSPE 2 will provide an open and dynamic forum for the community to discuss experiences and approaches in the areas listed above. This proposal requests funds to support attendance at WSSSPE 2 for US based researchers, particularly targeted at encouraging attendance by early stage researchers with attention to diversity.

@@

{\bf \noindent Broader Impacts:} All material from the workshop will be openly archived on public popular sites (e.g. Figshare, Slideshare, arXiv), it is anticipated that the workshop will again be Tweeted and Documented live including contributions from external participants. It is expected that the workshop will lead to a special issue of an open journal. The organizers take seriously the responsibility to encourage participation from underrepresented groups as workshop leaders as well as attendees, and NSF funds will be used to encourage such participation from the US community.

@@

%\newpage
%
%{\bf UNIVERSITY OF ILLINOIS AT URBANA-CHAMPAIGN}
%
%{\bf BUDGET JUSTIFICATION}
%
%{\bf WSSSPE2}
%
%{\bf Principal Investigator: Gabrielle Allen}
%
%\begin{enumerate}[label=\bf \Alph*.,leftmargin=*]
%
%\item {\bf Senior Personnel: } No funds requested.
%
%\item {\bf Other Personnel: } No funds requested.
%\item {\bf Fringe Benefits: }  No funds requested. 
%\item {\bf Equipment: }  No funds requested. 
%\item {\bf Travel: } \$3,000
%
%{\it National travel for the US based organizers to attend the workshop in New Orleans. Funds will be used to contribute towards airfares and/or the two hotel nights needed for the workshop}
%
%\item {\bf Participant Support: } \$20,000
%?{\it Funds are requested to support travel for 18 participants and 2 presenters from US institutions across the country to travel to New Orleans. Estimated costs include airfare, 2 nights hotel and workshop fees.}
%
%\item {\bf Other Direct Costs: } No funds requested. 
%\item {\bf Indirect Costs: } \$1,755
%
%{\it Indirect costs are assessed at a rate of 58.5\% of Modified Total Direct Costs (MTDC). MTDC is direct costs less equipment, tuition remission, and subawards in excess of \$25,000. }
%
%\item {\bf Total Costs: } \$24,755 
%
%{\it Total funds requested by this proposal. }
%
%
%\end{enumerate}
%
%\newpage
%
%{\bf Data Management Plan}
%
%As for WSSSPE1, all material (including publications, presentations, meeting minutes, real time discussions) will be open, hosted and archived on existing public platforms (e.g. Slideshare, ArXiv, Google Docs, Twitter). The WSSSPE web page and wiki will be additionally used.
%
%Reviews of paper submissions will not be open. 
%

>>>>

{\bf \noindent Summary:} The WSSSPE4 workshop is part of a community driven effort to address the many new challenges that are evident for the development, deployment, maintenance, and sustainabiity of reusable software for academic research and education. These challenges include the software development process, the support and maintenance of software, governance and business models particularly for sustainability, the role of software in building science communities, the need for software to lead to science which is verifiable and reproducible, policy issues such as how to measure software impact, choose licensing, or assign software credit, and the education and nurturing of early stage researchers in scientific software. 
Based on successful WSSSPE1-WSSSPE3 meetings at SC13, SC14, and NCAR in 2013, 2014, and 2015, the organizers expect over 60 submitted papers and around 75 attendees at the WSSSPE4 meeting that will be held immediately preceding the RSE conference in Manchester, UK, in September 2016.  As with previous events, WSSSPE4 will provide an open and dynamic forum for the community to discuss experiences and approaches in the areas listed above. This proposal requests funds to support attendance at WSSSPE4 for US based researchers, particularly targeted at encouraging attendance by early stage researchers with attention to diversity.

@@

{\bf \noindent Broader Impacts:} All material from the workshop will be openly archived on public popular sites (e.g. Figshare, Slideshare, arXiv), it is anticipated that the workshop will again be tweeted and documented live including contributions from external participants. It is expected that the workshop will lead to a special issue of an open journal. The organizers take seriously the responsibility to encourage participation from underrepresented groups as workshop leaders as well as attendees, and NSF funds will be used to encourage such participation from the US community.

@@

{\bf UNIVERSITY OF ILLINOIS AT URBANA-CHAMPAIGN}

{\bf BUDGET JUSTIFICATION}

{\bf WSSSPE2}

{\bf Principal Investigator: Gabrielle Allen}

\begin{enumerate}[label=\bf \Alph*.,leftmargin=*]

\item {\bf Senior Personnel: } No funds requested.

\item {\bf Other Personnel: } No funds requested.
\item {\bf Fringe Benefits: }  No funds requested. 
\item {\bf Equipment: }  No funds requested. 
\item {\bf Travel: } \$3,000

{\it National travel for the US based organizers to attend the workshop in New Orleans. Funds will be used to contribute towards airfares and/or the two hotel nights needed for the workshop}

\item {\bf Participant Support: } \$20,000
{\it Funds are requested to support travel for 18 participants and 2 presenters from US institutions across the country to travel to New Orleans. Estimated costs include airfare, 2 nights hotel and workshop fees.}

\item {\bf Other Direct Costs: } No funds requested. 
\item {\bf Indirect Costs: } \$1,755

{\it Indirect costs are assessed at a rate of 58.5\% of Modified Total Direct Costs (MTDC). MTDC is direct costs less equipment, tuition remission, and subawards in excess of \$25,000. }

\item {\bf Total Costs: } \$24,755

{\it Total funds requested by this proposal. }

\end{enumerate}

{\bf Data Management Plan}

As for WSSSPE1, all material (including publications, presentations, meeting minutes, real time discussions) will be open, hosted and archived on existing public platforms (e.g. Slideshare, ArXiv, Google Docs, Twitter). The WSSSPE web page and wiki will be additionally used.

Reviews of paper submissions will not be open.
